% Figure credits
\chapter{Required Figure Credits}
\label{ap: permissions}

\noindent
\textbf{Fig.~\ref{fig: intro-data}} --
Refs.~\cite{Ihee2001, Siwick2003, Baum2007, Ernstorfer2009},
reprinted with permission from AAAS;
Ref.~\cite{Eichberger2010}, reprinted with permission from Springer Nature;
Ref.~\cite{Zamponi2012}, copyright (2012) National Academy of Sciences.

\bigskip \noindent
\textbf{Fig.~\ref{fig: EDO-overview}} --
Refs.~\cite{BechgaardJerome1982, Dressel2007},
reprinted with permission from Springer Nature;
Ref.~\cite{Jerome1982}, reprinted with permission from Taylor \& Francis.

\bigskip \noindent
\textbf{Fig.~\ref{fig: EDO-static}} --
Ref.~\cite{Drozdova2003}, reprinted with permission, copyright \textsuperscript{\textcopyright{}} 2003
from Elsevier;
Ref.~\cite{Drozdova2004}, reprinted with permission, copyright (2004)
by the American Physical Society;
Ref.~\cite{Aoyagi2004}, reproduced with permission from The Royal Society of Chemistry.

\bigskip \noindent
\textbf{Fig.~\ref{fig: EDO-time-resolved}} --
Ref.~\cite{Chollet2004}, reprinted with permission from AAAS;
Ref.~\cite{Onda2008}, reprinted with permission, copyright (2008)
by the American Physical Society;
Refs.~\cite{Fukazawa2012, Onda2014}, reprinted with permission,
copyright (2012, 2014) American Chemistry Society.

\bigskip \noindent
\textbf{Fig.~\ref{fig: DAE-overview}} --
Ref.~\cite{Irie2014}, reprinted with permission, copyright (2014) American Chemistry Society.

\bigskip \noindent
\textbf{Fig.~\ref{fig: DAE-stilbene}} --
Ref.~\cite{Repinec1991}, reprinted with permission, copyright (1991) American Chemistry Society.

\bigskip \noindent
\textbf{Fig.~\ref{fig: DAE-PFC}} --
Refs.~\cite{Irie1995, Shibata2002}, reprinted with permission, copyright (1995, 2002) American Chemistry Society;
Ref.~\cite{Irie2001}, reprinted with permission from AAAS.

\bigskip \noindent
\textbf{Fig.~\ref{fig: DAE-PFC-TA}} --
Ref.~\cite{Jean-Ruel2011, Ward2012, Boggio2003}, reprinted with permission, copyright (2003, 2011, 2012) American Chemistry Society.

\bigskip \noindent
\textbf{Figs.~\ref{fig: DAE-PFC-Photo}--\ref{fig: DAE-PFC-results-QMQM}} --
Ref.~\cite{Jean-Ruel2013}, reprinted with permission, copyright (2013) American Chemistry Society; Ref.~\cite{Irie2001}, reprinted with permission from AAAS.

% \bigskip \noindent
% \textbf{Fig.~\ref{fig: DAE-PFC-structure}} --
% Ref.~\cite{Jean-Ruel2013}, reprinted with permission, copyright (2013) American Chemistry Society; Ref.~\cite{Irie2001}, reprinted with permission from AAAS.
%
% \bigskip \noindent
% \textbf{Fig.~\ref{fig: DAE-PFC-model}} --
% Ref.~\cite{Jean-Ruel2013}, reprinted with permission, copyright (2013) American Chemistry Society.
%
% \bigskip \noindent
% \textbf{Fig.~\ref{fig: DAE-PFC-QMQMmodel}} --
% Ref.~\cite{Jean-Ruel2013}, reprinted with permission, copyright (2013) American Chemistry Society; Ref.~\cite{Irie2001}, reprinted with permission from AAAS.
%
% \bigskip \noindent
% \textbf{Fig.~\ref{fig: DAE-PFC-UED}} --
% Ref.~\cite{Jean-Ruel2013}, reprinted with permission, copyright (2013) American Chemistry Society.
%
% \bigskip \noindent
% \textbf{Fig.~\ref{fig: DAE-PFC-UEDtraces}} --
% Ref.~\cite{Jean-Ruel2013}, reprinted with permission, copyright (2013) American Chemistry Society.
%
% \bigskip \noindent
% \textbf{Fig.~\ref{fig: DAE-PFC-results}} --
% Ref.~\cite{Jean-Ruel2013}, reprinted with permission, copyright (2013) American Chemistry Society.
%
% \bigskip \noindent
% \textbf{Fig.~\ref{fig: DAE-PFC-results-QMQM}} --
% Ref.~\cite{Jean-Ruel2013}, reprinted with permission, copyright (2013) American Chemistry Society.

\bigskip \noindent
\textbf{Fig.~\ref{fig: SCO-overview}} --
Refs.~\cite{Pauling1932a, Baker1964},
reprinted with permission, copyright (1932, 1964) American Chemistry Society.
Ref.~\cite{Dezsi1967}, reprinted with permission,
copyright \textsuperscript{\textcopyright{}} 1967 from Elsevier.

\bigskip \noindent
\textbf{Fig.~\ref{fig: SCO-theory}} --
Ref.~\cite{FiggisBook},
copyright \textsuperscript{\textcopyright{}} 1999, John Wiley \& Sons.

\bigskip \noindent
\textbf{Fig.~\ref{fig: SCO-tanabe}} --
Ref.~\cite{Tanabe1954b},
\textsuperscript{\textcopyright{}} 1954 The Physical Society of Japan;
Ref.~\cite{Marino2014},
\textsuperscript{\textcopyright{}} 2014 WILEY‐VCH Verlag GmbH \&~Co. KGaA, Weinheim;
Ref.~\cite{Ewald1964}, \textsuperscript{\textcopyright{}} 1964, Royal Society;
Ref.~\cite{Zimmermann1983},
copyright \textsuperscript{\textcopyright{}} 1983 from Elsevier;
Ref.~\cite{Ksenofontov1998},
copyright \textsuperscript{\textcopyright{}} 1998 from Elsevier.

\bigskip \noindent
\textbf{Fig.~\ref{fig: SCO-LIESST}} --
Ref.~\cite{Hauser1991a}, reproduced with the permission of AIP Publishing;
Ref.~\cite{Gutlich2012},
copyright \textsuperscript{\textcopyright{}} 2012 WILEY‐VCH Verlag GmbH \&~Co. KGaA, Weinheim;
Ref.~\cite{Deisenroth1994},
\textsuperscript{\textcopyright{}} J.C. Baltzer AG, Science Publishers 1994;
Ref.~\cite{Hauser1991c}, copyright \textsuperscript{\textcopyright{}} 1991 from Elsevier;
Ref.~\cite{Hauser2017}, reprinted with permission from Springer Nature.

\bigskip \noindent
\textbf{Fig.~\ref{fig: SCO-MLCT}} --
Ref.~\cite{Domingo2014}, reproduced with permission from The Royal Society of Chemistry.

\bigskip \noindent
\textbf{Fig.~\ref{fig: SCO-literature-TA}} --
Refs.~\cite{Monat2000, Gawelda2007a, Smeigh2008},
reprinted with permission, copyright (2000, 2007, 2008) American Chemistry Society.
Ref.~\cite{Aubock2015}, reprinted with permission from Springer Nature.

\bigskip \noindent
\textbf{Fig.~\ref{fig: SCO-literature-Xray}} --
Ref.~\cite{Henke1993}, copyright \textsuperscript{\textcopyright{}} 1993 Academic Press;
Refs.~\cite{Huse2011, March2017}, copyright (2011, 2017) American Chemistry Society;
Refs.~\cite{Rehr2000, Gawelda2007b},
reprinted with permission, copyright (2004) by the American Physical Society;
Ref.~\cite{Bressler2009}, reprinted with permission from AAAS;
Ref.~\cite{Zhang2014}, reprinted with permission from Springer Nature.

\bigskip \noindent
\textbf{Fig.~\ref{fig: SCO-literature-alt}} --
Ref.~\cite{Zhang2014}, reprinted with permission from Springer Nature;
Ref.~\cite{Tarnovsky2006}, copyright (2006) American Chemistry Society;
Ref.~\cite{Chang2010},
reprinted with permission, copyright (2010) by the American Physical Society;
Ref.~\cite{Sousa2013},
\textsuperscript{\textcopyright{}} WILEY-VCH Verlag GmbH \&~Co. KGaA, Weinheim;
Ref.~\cite{Sousa2018b}, reproduced with permission from the PCCP Owner Societies.

\bigskip \noindent
\textbf{Fig.~\ref{fig: BPY-intro}} --
Ref.~\cite{Sousa2013},
\textsuperscript{\textcopyright{}} WILEY-VCH Verlag GmbH \&~Co. KGaA, Weinheim;
Ref.~\cite{Zhang2018}, copyright (2018) American Chemistry Society.

\bigskip \noindent
\textbf{Fig.~\ref{fig: BPY-hostlattice}} --
Ref.~\cite{Sousa2013}, copyright \textsuperscript{\textcopyright{}} 2013 from Elsevier.

\bigskip \noindent
\textbf{Fig.~\ref{fig: AZA-intro}} --
Ref.~\cite{Ksenofontov1998},
copyright \textsuperscript{\textcopyright{}} 1998 from Elsevier;
Ref.~\cite{Capes2000}, \textsuperscript{\textcopyright{}} WILEY-VCH Verlag GmbH \&~Co. KGaA, Weinheim.

\bigskip \noindent
\textbf{Fig.~\ref{fig: future-molecules}} --
Ref.~\cite{Milek2013}, copyright (2013) American Chemistry Society;
Ref.~\cite{Venkataramani2011}, reprinted with permission from AAAS;
Ref.~\cite{Nihei2011}, reproduced with permission from The Royal Society of Chemistry.




% Chemistry in Action: Making Molecular Movies with Ultrafast Electron Diffraction and Data Science
